WIDS 2024 Final Project

### 2024-01-08 Code/R FIle.qmd
fixed header

---
title: "testibng"
format: html
editor: visual
---

@@

```{r}
head(union_wages)
head(union_states)
head(house)
head(income_distribution)
head(minimum_wage)
```
```{r}
range(union_wages$year) #ntl
range(union_states$year) # state
range(house$year) # state
range(income_distribution$year) # ntl
range(minimum_wage$year) # state
```

@@

#### State Dataframes
```{r}
full_state_data <- union_states |> 
  filter(sector == "Total") |> 
  select(-sector,
         -state) |> 
  left_join(house, by = c("year", "state_abbreviation")) |> 
  filter(party == "DEMOCRAT" | party == "REPUBLICAN") |> 
  mutate(decade = paste0((year - year %% 10), "s"),
         party_binary = ifelse(party == "DEMOCRAT", 1, 0)) |> 
  left_join(minimum_wage, by = c("year", "state")) |> 
  group_by(year, state) |> 
  mutate(party_state_avaerage = mean(party_binary)) |>
  ungroup()
```

>>>>

---
title: "WIDS 2024 Final Project"
author: "Michael Taffe, Melanie Klein, Ramiro Arevalo"
format: html
editor: visual
---

@@

```{r}
range(union_wages$year) #ntl
range(union_states$year) # state
range(house$year) # state
range(income_distribution$year) # ntl
range(minimum_wage$year) # state
```

@@

#### State Dataframes

```{r}
full_state_data <- union_states |> 
  filter(sector == "Total") |> 
  select(-sector,
         -state) |> 
  left_join(house, by = c("year", "state_abbreviation")) |> 
  filter(party == "DEMOCRAT" | party == "REPUBLICAN") |> 
  mutate(decade = paste0((year - year %% 10), "s"),
         party_binary = ifelse(party == "DEMOCRAT", 1, 0)) |> 
  left_join(minimum_wage, by = c("year", "state")) |> 
  group_by(year, state) |> 
  mutate(party_state_avaerage = mean(party_binary)) |>
  ungroup()
```
